---
title: "Data Wrangling Exercise"
author: "Your Name Here"
output: html
---

This is an Quarto document. It mixes text and code. It is great for annotating your analyses. It also creates beautiful documents in .html, .pdf, Word, and much more.

Below is the setup chunk. It runs, but nothing is "included" in your document. It is a good place to load packages and do other preliminary tasks.  

**Add the code that will load the `tidyverse` package.** 

```{r setup}
#| include: false
# Add the code to load the tidyverse package:


```

The data we will use is at this web URL:

https://github.com/wjschne/EDUC5529/raw/master/happiness.csv

Imagine that an intervention to increase happiness via counseling is given to 10 clients using a multiple baseline design just like in the tutorial.

Import the data into a variable called `d`:

```{r import}

```


View the data:

```{r view}

```


Filter to show only the row for the person for `id == 9`:

```{r filter9}

```


Select just variables for sessions 10 through 20:

```{r select20}

```


Restructure the data to make it longer and assign the long format to a variable called `d_longer`. Note that there are 100 sessions, not 60 like in the example.

```{r restructure}

```


Mutate the data to create a `phase` variable like in the tutorial's example:

```{r phase}

```


Now plot the data:

```{r plot}

```





